---
title: "smoothf.cpp"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

## Smoothf.cpp
Smoothf.cpp implements some smooth, differentiable approximations to max, min
and range. Tests of these functions are implemented in R with the Rcpp package.
Comparisons between actual min, max, and max-min are plotted.

```{r}
library(Rcpp)
sourceCpp("smoothf.cpp")

S_alpha(c(1,2,3,100),-10)#min
S_alpha(c(1,2,3,100),0)#mean
S_alpha(c(1,2,3,100),10)#max

LogSumExp(c(1,2,3,100),-10)#min
LogSumExp(c(1,2,3,100),10)#max

p_norm(c(1,2,3,100),100)#max abs
p_norm(c(1,2,3,-7),10)#max abs

smooth_range(c(1,2,3,100),10)#range

#actual
random_samples<-matrix(sample(100,100,replace=T),ncol=10)
mins<-apply(random_samples,2,min)
maxs<-apply(random_samples,2,max)
dranges<-apply(random_samples,2,function(x)diff(range(x)))
#smooth approximates
s.mins<-apply(random_samples,2,smooth_min)
s.maxs<-apply(random_samples,2,smooth_max)
s.dranges<-apply(random_samples,2,function(x)diff(smooth_range(x)))
plot(mins,s.mins)
abline(0,1)
plot(maxs,s.maxs)
abline(0,1)
plot(dranges,s.dranges)
abline(0,1)
```

The plots are approximately linear with slope 1 although the intercept does not appear to be zero
as you'd want. This is because it overestimates the minimum and underestimates the maximum.


